A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-03-17 review/answer_to_review.md

## Comments to the Author:

> I had the chance to read the manuscript entitled “Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data” authored by C. Schimd. This is an interesting paper that combines empirical analysis of Bronze age burial sites across Europe with a computer simulation of intergroup cultural transmission. The manuscript is well written, I enjoyed reading it, and think that the core findings are definitely of interest for archaeologist working on Bronze age Europe and for those interested in the application of cultural evolutionary framework. I am thus keen to recommend its publication, although I think several issues needs to be addressed before this.

> Firstly, my impression is that the author is trying to squeeze perhaps a bit too much in a single paper. I felt this was particularly the case of the computer simulation model which is almost thrown in in the mix, without much discussion on model parameters (see below). I would be tempted to suggest removing this entirely and include this into another paper.

After careful deliberation, I have decided to follow this advice. The simulation (1) does not add information that would be absolutely essential for the core topics, (2) reduces the overall comprehensibility due to the terminology that has to be introduced to describe it and (3) cannot be adequately presented and discussed here without leaving the initial scope of the paper. I will prepare another paper in the future that will present this simulation and other simulation approaches.

### 2019-03-17 README.Rmd
replaced key word
updated README accordingly

Bronze Age, Burial Traditions, Cultural Evolution, Cultural Transmission

@@

The `analysis` directory contains `code` and `data` to reproduce the preparations, calculations, simulations and figure renderings in this paper. The `article` directory contains the tex template and the text for the paper in *.Rmd* format.

>>>>

Bronze Age, Burial Traditions, Cultural Transmission, Radiocarbon Dating

@@

The `analysis` directory contains `code` and `data` to reproduce the preparations, calculations and figure renderings in this paper. The `article` directory contains the tex template and the text for the paper in *.Rmd* format.
